---
title: "Netflix_graphs"
author: "Vesa Kauppinen"
date: "3/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(plotly)
library(ggplot2)
library(lubridate)
library(data.table)
library(maps)
library(gganimate)
library(gifski)

dat<-read_csv('netflix_titles.csv')

dat %>% count(show_id)

dat$date_added <- mdy(dat$date_added)
dat$duration <- gsub("[^0-9.-]", "", dat$duration)
dat$duration <- as.numeric(dat$duration)

```
## Data 

The data used is Kaggle dataset consisting of TV shows and movies listed on Netflix https://www.kaggle.com/shivamb/netflix-shows.


## Graph 1: Cumulative number of shows added into Netflix by date and type of show

Below graph shows a cumulative number of shows into Netflix by date and the type of show (Movies/TV Shows)).

```{r g1, echo=FALSE}
movies <- dat %>% select(show_id, date_added, type) %>% group_by(date_added, type) %>%
 filter(type=='Movie') %>% summarise(nbr_shows = n())
movies$Movies <- cumsum(movies$nbr_shows)
movies <- movies %>% select(date_added,Movies)

tv_shows <-  dat %>% select(show_id, date_added, type) %>% group_by(date_added, type) %>%
        filter(type=='TV Show') %>% summarise(nbr_shows = n())
tv_shows$TV_shows <- cumsum(tv_shows$nbr_shows)
tv_shows <- tv_shows %>% select(date_added,TV_shows)

dat2 <- merge(x = tv_shows, y =movies, by = "date_added", all = TRUE)



dat3 <- data.table(dat2)

setnafill(dat3, type = "locf")

dat3_long <- gather(dat3,type, count, TV_shows:Movies,factor_key = TRUE)
ggplot(dat3_long, aes(x=date_added, y=count, fill=type)) + geom_area() +ylim(0,10000) + 
        xlab('Date') + ggtitle('Cumulative count of shows added into Netflix')

```

## Graph 2: Number of shows by their release year.

The below histogram shows the number of shows available in Netflix by their release year.

```{r 2, echo=FALSE}
ggplot(dat, aes(x=release_year)) + geom_histogram(bins=100) + ggtitle('Count of shows in Netflix by the release year') + xlab('Release year')
```

## Graph 3: Duration of movies and TV shows

Below figure shows a boxplot presentation of distributions of durations of movies (in mins) and TV shows (in number of seasons) in Netflix.

```{r 3, echo=FALSE}

ggplot(dat, aes(x=type, y=duration, fill=type)) + geom_boxplot() + facet_wrap(~type, scales="free") +
        ggtitle("Duration of movies (minutes) and TV shows (seasons) in Netflix") + xlab("")

```

## Graph 4: Number of shows in Netflix by the country of origin

Below plotly presentation shows the number of shows in Netflix by the origin country.


```{r 4, echo = FALSE}
dat_country <- dat %>% group_by(country) %>% summarise(count = n()) %>% 
 rename (region=country)
dat_country$region[dat_country$region=='United States'] <- 'USA'
dat_country$region[dat_country$region=='United Kingdom'] <- 'UK'
my_world_map <- map_data("world")
map_data_combined <- left_join(my_world_map, dat_country,by='region')
ggplotly(ggplot(data=map_data_combined, mapping=aes(x=long, y=lat,group=group, fill=count))+
        geom_polygon() + scale_colour_brewer(palette = "Set1") +
        ggtitle('Number of shows by origin country'))
```

## Graph 5: Count of shows by rating in Netflix

Below graph shows ount of shows by rating in Netflix

```{r 5, echo=FALSE}

flix2 <- dat %>%  select(show_id, rating, type) %>% 
        group_by(rating) %>% summarise(count= n())

 ggplot(flix2, aes(x=reorder(rating,count), y=count)) + geom_bar(stat='identity') +
        coord_flip() + xlab('Rating') + ggtitle('Count of shows by rating') 

```

## Graph 6: Median duration of movies from USA, UK and India by the year of release

Below graph shows th median duration of movies from USA, UK and India available in Netflix by the year of release.


```{r 6, echo = FALSE}
dur_dat <- dat %>% filter(type == 'Movie') %>% select(duration, release_year,show_id,country) %>%
        filter(country %in% c('United States','United Kingdom','India')) %>%
        group_by(release_year) %>% mutate(median_duration = median(duration))

ggplot(dur_dat, aes(x=release_year,y=median_duration, color=country)) + geom_point() +
        geom_smooth(method='lm') +
       xlab('Release year') +   scale_color_manual(values=c('red','blue','green')) +
        ggtitle('Median duration of movies by selected origin countries by the year released') +
        ylab('Median movduration (mins)')
```

## Graph 7: Number of shows in Netflix by release from selected origin countries.

Number of shows in Netflix by release from selected origin countries.


```{r 7, echo=FALSE}
dur_dat1 <- dat %>% filter(type == 'TV Show', release_year >= 2000) %>% select(duration, release_year,show_id,country) %>%
        filter(country %in% c('United States','United Kingdom','India','Japan')) %>%
        group_by(show_id,release_year,country) %>% summarise(count = n())

my_anim <- ggplot(dur_dat1, aes(x=release_year,y=count, fill=country)) + geom_bar(stat='identity') + transition_states(country) + exit_fade() + enter_fade()+xlab('Release year')+
        ggtitle('Number of shows by release year')
my_anim
```

## Graph 8: Average duration of Netflix TV shows by release year

Average duration of Netflix TV shows by release year (2000-2021) from selected origin countries.

```{r 8, echo=FALSE}
dur_dat2 <- dat %>% filter(type == 'TV Show', release_year >= 2000) %>% 
        filter(country %in% c('United States','United Kingdom','India','Japan')) %>%
        select(release_year,country,duration) %>%
        group_by(release_year,country) %>% summarise(mean_duration = mean(duration))

my_anim2 <- ggplot(dur_dat2, aes(x=release_year, y=mean_duration, fill=country)) + geom_bar(stat='identity') +  transition_states(country) + exit_fade() + enter_fade() + 
        xlab('Release year') + ylab('Averega duration (seasons)') +
        ggtitle('Average duration of Netflix TV shows by release year')
my_anim2
```

